A note on multi agent learning

### 2016-06-27 multiAgentLearning/paper/article.tex
todoing

\abstract{
  %TODO abstract
	abstract..
}

\section{Introduction}

Satisficing play was originally introduced
to try and limit the computation power that earlier models required of human
behavior \citep{herbert}. Originating from the field of economics, they
wanted to use a model that was not ``super intelligent''.

The classical models from the field of economics had at least one of the
following assumptions:

\begin{itemize}
\itemsep0em 
  \item The structure of the game is known.
  \item Awareness of other player's decisions.
  \item Awareness of being in a game situation
  \item Being able to preform maximization calculations.
\end{itemize}

@@

\section{Core algorithm}
The core algorithm as presented by \citep{herbert} and formalized by
\citep{karandikar}
can be seen bellow:

@@

\section{Iterated prisoners dilemma}
[To be extended]

To demonstrate a potential use of this algorithm we will use at several example
cases. The first one being the iterated prisoners dilemma. Consider
the following normal form game:

@@

...

@@

...
\section{Properties of satisifing play}
[To be extended]

@@

\section{An extended satisficing play}
[To be extended]

@@

\section{Satisficing compared to other learning methods}
With help of the work of \citep{crandall} saticificing play is compared
to Q-learning and WOLF-PHC.
Q-learning is explained briefly with help of \citep{sandholm} and WOLF-PHC
with help of \citep{bowling}.

>>>>

\abstract{
  %TODO abstract
  \todo[inline]{abstract missing}
}
\section{Introduction}
\toReview
Satisficing play was originally introduced
to try and limit the computation power that earlier models required of human
behavior \citep{herbert}. Originating from the field of economics, they
wanted to use a model that was not ``super intelligent''.

The classical models from the field of economics had at least one of the
following assumptions:
\begin{itemize}
\itemsep0em 
  \item The structure of the game is known.
  \item Awareness of other player's decisions.
  \item Awareness of being in a game situation
  \item Being able to preform maximization calculations.
\end{itemize}

@@

\section{Core algorithm}
The core algorithm as presented by \citep{herbert} and formalized by
\citep{karandikar} \todo[inline]{karandikars algorithm is different..}
can be seen bellow:

@@

\section{Iterated prisoners dilemma}
\drafting
To demonstrate a potential use of this algorithm we will use at several example
cases. The first one being the iterated prisoners dilemma. Consider
the following normal form game:

@@

\todo{copy table}

@@

\todo{copy table}
\section{Properties of satisifing play}
\drafting

@@

\section{An extended satisficing play}
\drafting

@@

\section{Satisficing compared to other learning methods}
\drafting
With help of the work of \citep{crandall} saticificing play is compared
to Q-learning and WOLF-PHC.
Q-learning is explained briefly with help of \citep{sandholm} and WOLF-PHC
with help of \citep{bowling}.
